A Lock-Free Interaction Combinator Evaluator

### 2023-09-08 paper/draft.tex
:|

A specific type of interaction nets is the system called \textit{interaction combinators}, introduced by Lafont~\cite{lafont1997interaction}. These are built from three types of nodes: constructor (CON), duplicator (DUP), and eraser (ERA). Each node has a principal port and two auxiliary ports. The nodes interact according to six rules, divided into two categories: commutation and annihilation. Commutation rules apply when two different types of nodes are connected through their principal ports, while annihilation rules apply when two nodes of the same type are connected through their principal ports. In this paper, we use the symmetric interaction combinator variant, which has been described by Mazza~\cite{mazza2007denotational}, and is illustrated below:

>>>>

A specific type of interaction nets is the system called \textit{interaction combinators}, introduced by Lafont~\cite{lafont1997interaction}. These are built from three types of nodes: constructor (CON), duplicator (DUP), and eraser (ERA). Each node has a principal port and two auxiliary ports. The nodes interact according to six rules, divided into two categories: commutation and annihilation. Commutation rules apply when two different types of nodes are connected through their principal ports, while annihilation rules apply when two nodes of the same type are connected through their principal ports. In this paper, we use the symmetric interaction combinator variant, which has been described by Mazza~\cite{mazza2007denotational}, and is illustrated below.
